State of the Practice for Medical Imaging Software Based on Open Source Repositories

### 2024-11-10 StateOfPractice/Papers/SOP_MI_CritReviewsBioMedEng/SOP_MI_OSR.tex
Revisiong to Section 9 (Software Qualities)

Synthesizing the feedback from the interviewees, it is clear that increased
connections between the development team and medical professionals/institutions
could improve testing effectiveness and thus increase correctness.

@@

The structured interviews also included an active discussion of software
qualities, and in particular maintainability and reproducibility. Note that
these did not come up as ``pain points''.
%\cite{SmithEtAl2021}.  
The developers discussed their approaches for improving these qualities, which
we now relay.

@@

The main strategy is to reduce code duplication by using properly structured
libraries.  Other strategies mentioned include supporting third-party
extensions, an easy-to-understand architecture, a dedicated architect, starting
from simple solutions, and documentation.

\item[Q\refstepcounter{qnum}\theqnum \label{Q_Reproducibility}:]
\textbf{Reproducibility:}  
An important precondition for reproducibity is increased and better
documentation (which also helps with many of the afore mentioned pain points).
The challenges of inadequate documentation are a known problem for research
software \cite{PintoEtAl2018, WieseEtAl2019} and for non-research software
\cite{LethbridgeEtAl2003} alike.

>>>>

@@

The structured interviews also included an active discussion of software
qualities, in particular maintainability and reproducibility. This
discussion did not come up as ``pain points'', but rather through
planned questions we asked for improving these qualities.

@@

The main strategy mentioned to reduce code duplication is using properly structured
libraries.  Other strategies mentioned include supporting third-party
extensions, an easy-to-understand architecture, a dedicated architect, starting
from simple solutions, and documentation.

\item[Q\refstepcounter{qnum}\theqnum \label{Q_Reproducibility}:]
\textbf{Reproducibility:}  
An important precondition for reproducibility is increased and better
documentation (which also helps with many of the aforementioned pain points).
The challenges of inadequate documentation are a known problem for research
software \cite{PintoEtAl2018, WieseEtAl2019} and for non-research software
\cite{LethbridgeEtAl2003} alike.
